---
title: "AFDHS preliminary data analysis"
---

# Getting started

Here we show the pre-requisite code sections. Run these at the outset to avoid errors. First we load the required packages.

```{r}
#| label: load-packages
#| echo: true
#| output: false

easypackages::libraries(
    
    # Data i/o
    "here",                 # relative file path
    "rio",                  # file import-export
    
    # Data manipulation
    "janitor",              # data cleaning fns
    "haven",                # stata, sas, spss data io
    "labelled",             # var labelling
    "readxl",               # excel sheets
    # "scales",               # to change formats and units
    "skimr",                # quick data summary
    "broom",                # view model results
    
    # Data analysis
    "DHS.rates",            # demographic rates for dhs-like surveys
    "GeneralOaxaca",        # BO decomposition for non-linear
    "survey",               # apply survey weights
    "survival",             # base pkg for survival analysis
    
    # Analysis output
    "gt",
    # "modelsummary",          # output summary tables
    "gtsummary",            # output summary tables
    "flextable",            # creating tables from objects
    "officer",              # editing in office docs
    
    # R graph related packages
    "ggstats",              # graph of regression estimates
    "RColorBrewer",         # graph themes
    # "scales",
    "patchwork",            # combining graphs
    
    # Misc packages
    "tidyverse",            # Data manipulation iron man
    "tictoc"                # Code timing
)

```

Next we turn off scientific notations.

```{r}
#| label: turn-off-scientific-notation
#| echo: true
#| output: false
 
options(scipen = 999)

```

Next we set the default gtsummary print engine for tables.

```{r}
#| label: set-gtsummary-default
#| echo: true
#| output: false 

theme_gtsummary_printer(print_engine = "flextable")

```

Now we set the flextable output defaults.

```{r}
#| label: set-flextable-default
#| echo: true
#| output: false 

set_flextable_defaults(
  font.size = 11,
  text.align = "left",
  big.mark = "",
  background.color = "white",
  table.layout = "autofit",
  theme_fun = theme_vanilla
)

```

# Document introduction

In this document we do preliminary analysis of examining infant mortality clustering under mothers in the pooled Afghanistan Demographic and Health Survey (AFDHS) datasets. This document has selected code for analysis and the full spectrum of preliminary analysis are available in the "afdhs_datanal1.R" script file.

## Data source

Here we use the pooled dataset of one existing round of Afghanistan Demographic and Health Survey (AFDHS) conducted during 2015. The AFDHS implemented a multi-stage cluster sampling design. Details regarding the sample design, survey instruments, informed consent, training of interviewers and other fieldwork officers, data collection and processing, and response rates are available in the final report of the respective surveys.

We pooled the raw birth histories of ever-married women in the reproductive age group (15-49 years) across all the pre-specified rounds. We manually harmonized all required datasets so that our study variables have consistent categorisation and label codes across the surveys. The pooled dataset harmonization and pooling codes are in "afdhsv2_daprep.R". Also, we have a variable harmonization documentation called "afdhs_datapl1_pre.html" which shows how the variable labels and label codes vary across the raw AFDHS datasets.

Now, please note that the following Afghanistan DHS surveys were pooled:

```{r}
#| label: tbl-detail-survey-rounds
#| echo: true
#| output: true
#| tbl-cap: "Afghanistan DHS datasets and their sample size to be used for pooling"

# Importing the afbr nested tibble
afbr1_tmp_intro <- read_rds(
    file = here("website_data", "afbr1_nest0.rds")
)
# Importing the afhr nested tibble
afhr1_tmp_intro <- read_rds(
    file = here("website_data", "afhr1_nest0.rds")
)
# Importing the afpr nested tibble
afpr1_tmp_intro <- read_rds(
    file = here("website_data", "afpr1_nest0.rds")
)

# Creating the table of surveys to be used for pooling
afbr1_tmp_intro |> select(c(ctr_name, svy_year, n_births)) |> 
    # Join vars from afhr_tmp_intro
    left_join(
        afhr1_tmp_intro |> select(svy_year, n_households),
        by = join_by(svy_year)
    ) |> 
    # Join vars from afpr_tmp_intro
    left_join(
        afpr1_tmp_intro |> select(svy_year, n_persons),
        by = join_by(svy_year)
    ) |> 
    # convert nested tibble to simple tibble
    unnest(cols = c()) |> 
    mutate(
        ccode = row_number(), 
        .before = ctr_name
    ) |> 
    # convert to flextable object
    qflextable() |> 
    theme_vanilla() |> 
    align(align = "left", part = "all")

```

**Note that** the information on birth histories was available for 164,761 children. The current study utilised pooled retrospective birth histories of children born between 1970 to 2022 (till the interview date). Therefore, the analytical sample size of this study is 163,544 children.

```{r}
#| label: just-another-chunk01
#| echo: false
#| output: false

# We remove the (.)_tmp_intro nested tibbles from the environment as they are not 
# required further
rm(list = c("afbr1_tmp_intro", "afhr1_tmp_intro", "afpr1_tmp_intro"))

# Reclaim unused space
gc()

```

## Study variables

We use the following variables for the pooled data analysis:

-   **Dependent variable**
    -   infantd = Index child died during infancy period (0-11 months)
-   **Main Independent variable**
    -   sibsurv_nmv = Survival status of preceding child (Death scarring)
    -   binterval_3c_nmv_opp = Birth interval preceding to index child
-   **Independent variables \[CHILD LEVEL\]**
    -   cyob10y_opp = Birth cohort of index child
    -   bord_c = Birth order of index child
    -   sex_fm = Sex of index child
    -   season = Season during birth
-   **Independent variables \[MOTHER/PARENT LEVEL\]**
    -   ~~myob_opp = Birth cohort of mother~~
    -   macb_c_opp = Mother's age during birth of index child
    -   medu_opp = Mother's Level of education
    -   pedu_opp = Father's level of education
-   **Independent variables \[HOUSEHOLD LEVEL\]**
    -   ~~religion = Religion~~
    -   ~~nat_lang = Native language of respondent~~
    -   wi_qt_opp = Household wealth quintile
    -   ~~hhgen_2c_opp = Generations in household~~
    -   hhstruc_opp = Household structure
    -   head_sex = Sex of HH head
-   **Independent variables \[COMMUNITY LEVEL\]**
    -   por = Place of residence of the household
    -   ~~ecoreg = Ecological region~~

*Note: (a) Crossed names indicates variable not included.*

## Statistical methods

We first conducted descriptive analysis to examine the absolute and percentage distribution of births by background characteristics in the pooled dataset. Next we explored the distribution of infant mortality by birth cohorts and survey periods. Also, we examined the trend in childhood mortality (neonatal, infant and under-five mortality) rates across the Afghanistan DHS survey rounds. Next, we performed bivariate analysis to assess the unadjusted relationship between infant mortality and the main independent variables using the chi-square test for association. To estimate the adjusted associations, we applied multivariable logistic regression models on the pooled dataset covering 1970-2022.

# Data import

We will directly import the prepared dataset for analysis here. The code for dataset preparation is in the "afdhsv2_daprep.R" script file.

```{r}
#| label: data-import
#| echo: true
#| output: true

# Importing the pooled afbr tibble
afbr1_pl1 <- read_rds(
    file = here("website_data", "afbr1_pl1.rds")
)

# Prepare the survey weighted dataset
options(survey.lonely.psu = "adjust")
options(survey.adjust.domain.lonely = T)
svy_afbr1_pl1 <- svydesign(
    data = afbr1_pl1,
    ids = ~ as.numeric(svy_psu),
    strata = ~ as.numeric(svy_strata),
    weight = ~ svy_wwgt6,
    probs = NULL,
    nest = T
)

```

# Descriptive analysis

## Sample distribution of births

We will check the distribution of births by background characteristics in Afghanistan 1970-2022.

```{r}
#| label: univariate-dist-ut
#| echo: false
#| output: false

# First we create the variable list
vlist_t1 <- c("sibsurv_all_nmv", "sibsurv_3c_nmv", "binterval_3c_nmv_opp", 
              "cyob10y_opp", "bord_c", "sex_fm", "season", "macb_c_opp", 
              "medu_opp", "pedu_opp", "wi_qt_opp", 
              "hhstruc_opp", "head_sex", "por")

# Univariate table - unweighted
t1_ut <- afbr1_pl1 |> 
    tbl_summary(
        include = all_of(vlist_t1),
        digits = everything() ~ c(0, 1)
    ) |>
    # Table title
    # modify_caption("**Table S1: Sample distribution of births by background characteristics in Afghanistan 1970-2022**") |> 
    bold_labels()
t1_ut

```

```{r}
#| label: univariate-dist-wt
#| echo: false
#| output: false

# Univariate table - weighted
t1_wt <- svy_afbr1_pl1 |> 
    tbl_svysummary(
        include = all_of(vlist_t1),
        # statistic = everything() ~ "{p}%",
        digits = everything() ~ c(0, 1)
    ) |> 
    bold_labels()
t1_wt

```

```{r}
#| label: tbl-univariate-dist-utwt
#| echo: true
#| output: true
#| tbl-cap: "Distribution of births by background characteristics in Afghanistan 1970-2022"

# Now, we merge the unweighted and weighted tables and view it
t1 <- tbl_merge(
    tbls = list(t1_wt, t1_ut),
    tab_spanner = c("**Weighted**", "**Unweighted**")
) |> 
    modify_footnote(
        stat_0_1 ~ "n (%) = Distribution and column percentage (weighted);",
        stat_0_2 ~ "n (%) = Distribution and column percentage (unweighted)"
    ) |> 
  as_flex_table() |> 
  theme_vanilla()
t1

```

@tbl-univariate-dist-utwt presents the sample characteristics of all births from the complete birth histories of Afghanistan from 1970 to 2022. The distribution of our two main explanatory variables, shows that there were 11% children whose previous sibling had died before their birth. Most children in Afghanistan had a preceding birth interval of 24 months or more. Among the children considered in the study, the majority were from the 1990-99 birth cohort (35.5%), followed by the 2000-09 cohort (23.1%) and the 1980-89 cohort (22.7%). More than half of the children were male (51.2%) and belonged to the first or second birth order (56.4%).

Almost 38% of children were born when their mothers were aged 20-24 years, followed by 24% whose mothers were less than 20 years old. Nearly 71% of mothers and 36% of fathers had no formal schooling. Most households practised Hinduism (84.8%), and Afghani was the primary language spoken in almost 46% of households. The majority of children lived in rural areas (75.7%) and in the Terai region (52.7%), followed by the Hill region (40%) and the Mountain region (7.3%).

## Distribution of infant deaths by birth cohort and survey period

Here we prepare the data of infant mortality by birth cohort. Using the data we prepare the graph of distribution of infant deaths by birth cohort. Unlike other South Asian countries we do not estimate distribution by survey period as there is a single survey for Afghanistan.

```{r}
#| label: data-infantd-birth-cohort
#| echo: false
#| output: false
#| warning: false

# First, we create the gtsummary table
f1_cohort_gtsum <- svy_afbr1_pl1 |> 
    tbl_svysummary(
        include = cyob5y,
        by = infantd,
        statistic = all_categorical() ~ "{p}",
        digits = all_categorical() ~ 1,
        percent = "row"
    ) 

# Second, we convert the gtsummary object to tibble.
f1_cohort_tibble <- f1_cohort_gtsum |> 
    as_tibble() |> 
    slice(-1) |> 
    rename(
        "birth_cohort" = 1,
        "pct_alive" = 2,
        "pct_dead" = 3
    ) |> 
    mutate(
        birth_cohort = birth_cohort |> fct() |> fct_rev(),
        across(.cols = c(pct_alive, pct_dead), as.numeric)
    )
f1_cohort_tibble

```

```{r}
#| label: fig-infantd-birth-cohort
#| echo: true
#| output: true
#| fig-cap: "Lollipop chart showing the weighted percentage of infant deaths by birth cohort in Afghanistan DHS"

# Let's create the lollipop chart.
fig1_cohort <- f1_cohort_tibble |> 
    ggplot(aes(y = birth_cohort, x = pct_dead)) +
    
    # adding line segment or lollipop stick
    geom_segment(
        aes(x = 0, xend = pct_dead, y = birth_cohort, yend = birth_cohort),
        linewidth = 2,
        colour = "green4"
    ) +
    
    # adding the point or lollipop head
    geom_point(
        shape = 21,
        size = 15,
        fill = "white",
        colour = "green4"
    ) +
    
    # adding the percentage text
    geom_text(
        aes(label = pct_dead),
        fontface = "bold"
    ) +
    
    labs(
        # title = "(A) By Birth cohort",
        x = "Weighted percentage of children",
        y = "Birth cohort",
    ) +
    
    theme(
        plot.title = element_text(size = rel(1.3), face = "bold"),
        # plot.subtitle = element_text(size = rel(1.2)),
        axis.title.x = element_text(size = rel(1.2)),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = rel(1.2)),
        axis.text.y = element_text(size = rel(1.2))
    )
fig1_cohort

```

@fig-infantd-birth-cohort further highlights the temporal shifts in infant mortality across different birth cohorts. The results indicate a steady decline in infant mortality over time, with higher mortality rates in earlier birth cohorts (1970–1979), which gradually decreased in the subsequent cohorts. The most recent cohorts (2010 and later) exhibit the lowest mortality rates, reflecting improvements in child survival over the decades.

# Bivariate analysis

## Crosstab of infant mortality by background characteristics

Here we will check the crosstab tables of infant mortality with the independent variables using row percentages and check their association with the chi-square test.

```{r}
#| label: tbl-bivariate-infantd-wt
#| echo: true
#| output: true
#| warning: false
#| tbl-cap: "Distribution of infant deaths by background characteristics among Afghani children from 1970-2022"

# Creating the var list
vlist_t2 <- c("infantd", "sibsurv_3c", "binterval_3c_opp", 
              "cyob10y_opp", "bord_c", "sex_fm", "season", "macb_c_opp", 
              "medu_opp", "pedu_opp", "wi_qt_opp", 
              "hhstruc_opp", "head_sex", "por")

# Prepare the weighted gtsummary table
t2_wt <- svy_afbr1_pl1 |> 
  tbl_svysummary(
    include = all_of(vlist_t2),
    by = infantd,
    percent = "row"
  ) |> 
  add_overall(statistic = ~ "{n}") |> 
  add_p() |> 
  
  # hide the alive col
  modify_column_hide(columns = stat_1) |> 
  # Add extra header
  modify_spanning_header(
    c(stat_2, p.value) ~ "**Infant mortality (0-11 months)**"
  ) |> 
  modify_footnote(
    all_stat_cols() ~ "n = Absolute distribution; % = Row percentage; Adjusted for sampling weights"
  ) |> 
  # styling
  bold_labels() |> 
  bold_p(t = 0.05) |> 
  as_flex_table() |> 
  theme_vanilla()
t2_wt                           # view table

```

@tbl-bivariate-infantd-wt shows that among children whose preceding sibling died before their conception, 15% experienced infant mortality. Mortality was also higher for children whose previous sibling died after their conception. Infant mortality varied significantly across birth intervals, birth cohorts, and parental characteristics. Mortality was highest among children born within 18 months of a previous birth, with 21% experiencing infant mortality. In contrast, children born after between 25-29 years had the lowest mortality rate of 6.8%. Sex differences were minor, with female infant mortality at 7.7% and male mortality at 8.7%.

# Multivariable analysis

## Regression of infant deaths by background characteristics

Here we will check the multivariable association of infant mortality with the independent variables by estimating logistic regression models. We run the weighted regression models by:

-   Model 1: Without main independent variables.
-   Model 2: With main independent variables.

```{r}
#| label: model-infantd-logit-1
#| echo: false
#| output: false

# First we run the weighted regression model without main independent variables
log_mdl1 <- svyglm(
    infantd_01 ~ cyob10y_opp + bord_c + sex_fm + season + 
        macb_c_opp + medu_opp + pedu_opp + 
        wi_qt_opp + hhstruc_opp + head_sex + 
        por,
    design = svy_afbr1_pl1,
    family = quasibinomial(link = "logit")
)

```

```{r}
#| label: table-infantd-logit-1
#| echo: false
#| output: false

# Converting the regression model output using gtsummary
t3_log_mdl1 <- log_mdl1 |> 
    tbl_regression(exponentiate = T) |> 
    add_glance_table(include = c(nobs, AIC, BIC)) |> 
    add_vif(statistic = "GVIF") |> 
    modify_spanning_header(
        c(estimate, conf.low, p.value, GVIF) ~ "**Model-1**"
    ) |> 
    bold_labels() |> 
    bold_p(t = 0.1)
t3_log_mdl1

```

```{r}
#| label: model-infantd-logit-2
#| echo: false
#| output: false

# Second we run the weighted regression model with main independent variables
log_mdl2 <- svyglm(
    infantd_01 ~ sibsurv_3c + binterval_3c_opp + cyob10y_opp + bord_c +
        sex_fm + season + macb_c_opp + medu_opp + pedu_opp + 
        wi_qt_opp + hhstruc_opp + head_sex + 
        por,
    design = svy_afbr1_pl1,
    family = quasibinomial(link = "logit")
)

```

```{r}
#| label: table-infantd-logit-2
#| echo: false
#| output: false

# Converting the regression model output using gtsummary
t3_log_mdl2 <- log_mdl2 |> 
    tbl_regression(exponentiate = T) |> 
    add_glance_table(include = c(nobs, AIC, BIC)) |> 
    add_vif(statistic = "GVIF") |> 
    modify_spanning_header(
        c(estimate, conf.low, p.value, GVIF) ~ "**Model-2**"
    ) |> 
    bold_labels() |> 
    bold_p(t = 0.1)
t3_log_mdl2

```

```{r}
#| label: tbl-infantd-logit-12
#| echo: true
#| output: true
#| tbl-cap: "Multivariable association of infant mortality and the independent variables among children in Afghanistan 1970-2022"

# We merge the model-1 and model-2 tables
t3_log <- tbl_merge(
    tbls = list(t3_log_mdl1, t3_log_mdl2),
    tab_spanner = c("**Model-1**", "**Model-2**")
) |> 
    # ensure that estimates of sibsurv_3c and binterval_3c_opp are at the top
    modify_table_body(
        ~ .x |> 
            arrange(desc(variable %in% c("sibsurv_3c", "binterval_3c_opp")))
    )
# Now we view the table
t3_log |> 
  as_flex_table() |> 
  fontsize(size = 9, part = "all") |> 
  theme_vanilla()

```

@tbl-infantd-logit-12 presents the results of the logistic regression analysis, showing key factors associated with infant mortality. Afghani children whose preceding sibling had died before their conception had 1.86 times higher odds of experiencing infant mortality. Short birth intervals, particularly those under 18 months, were associated with a significantly higher risk, with mortality odds 2.51 times higher than for births with a preceding interval of 24 months or longer.

## START FROM HERE

UPCOMING TASKS:

-   Run survival regression models and check the result.

-   Check if frailty survival regression models can be run.

-   Check and apply the evalue package.

TO BE CONTINUED ...

