---
title: "Pooled DHS data dictionary"
---

# Getting started

First we load the required packages.

```{r}
#| label: load-packages
#| echo: true
#| output: false

easypackages::libraries(
  # Data i/o
  "here",                 # relative file path
  "rio",                  # file import-export
  
  # Data manipulation
  "janitor",              # data cleaning fns
  "haven",                # stata, sas, spss data io
  "labelled",             # var labelling
  "readxl",               # excel sheets
  # "scales",               # to change formats and units
  "skimr",                # quick data summary
  "broom",                # view model results
  
  # Analysis output
  "gt",
  # "modelsummary",          # output summary tables
  "gtsummary",            # output summary tables
  "flextable",            # creating tables from objects
  "officer",              # editing in office docs
  
  # R graph related packages
  "ggstats",
  "RColorBrewer",
  # "scales",
  "patchwork",
  
  # Misc packages
  "tidyverse",            # Data manipulation iron man
  "tictoc"                # Code timing
)

```

Next we turn off scientific notations.

```{r}
#| label: turn-off-scientific-notation
#| echo: true
#| output: false

options(scipen = 999)

```

Next we set the default gtsummary print engine for tables.

```{r}
#| label: set-gtsummary-default
#| echo: true
#| output: false 

theme_gtsummary_printer(print_engine = "flextable")

```

Now we set the flextable output defaults.

```{r}
#| label: set-flextable-default
#| echo: true
#| output: false 

set_flextable_defaults(
  font.size = 11,
  text.align = "left",
  big.mark = "",
  background.color = "white",
  table.layout = "autofit",
  theme_fun = theme_vanilla
)

```

# Document introduction

We document the variable labels and other contents of all variables across all the pooled Demographic and Health Survey (DHS) birth history datasets of South Asian countries here. This will be primary document for viewing what variables will be used for analysis in PhD research. This document will guide us on the variable availability in the pooled datasets of the various South Asian countries.

This document contains variable details for the following Afghanistan DHS surveys:

```{r}
#| label: data-import
#| echo: false
#| output: false

# Importing the pooled dataset of sasiadhs countries
# Importing the Bangladesh DHS pooled dataset
bdbr_pl <- read_rds(
  file = here("website_data", "bdbr1_pl1.rds")
)
# Importing the Nepal DHS pooled dataset
npbr_pl <- read_rds(
  file = here("website_data", "npbr1_pl1.rds")
)

```

```{r}
#| label: tbl-detail-survey-rounds
#| echo: true
#| output: true
#| tbl-cap: "South Asian DHS datasets and their sample size to be used for pooling"

# Creating the table of pooled surveys to be used for analysis
sasiadhs_tbl <- tibble(
  ccode = c(1:2),
  country = c("Bangladesh", "Nepal"),
  n_sample = c(nrow(bdbr_pl), nrow(npbr_pl)),
  n_variables = c(ncol(bdbr_pl), ncol(npbr_pl))
)

# Convert and view as flextable
sasiadhs_tbl |> 
  mutate(n_sample = prettyNum(n_sample, big.mark = ",")) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

Here we will create basic data dictionaries of each datasets using the labelled package. In our earlier efforts we realized that the method for generation data dictionaries for each dataset are similar. Hence, we will create a function using the look_for() command to generate the data dictionaries and view them.

```{r}
#| label: fn-gen-dadict
#| echo: false
#| output: false

# We create a function for generating basic data dictionary
dadict_basic <- function(df) {
  df |> 
  # create data dictionary
  labelled::lookfor(details = "basic") |> 
  # keep only the required columns
  select(-c(pos, levels, value_labels)) |> 
  # for correctly viewing the range column in data dictionary
  labelled::convert_list_columns_to_character()
}

```

# Bangladesh DHS pooled data dictionary

Here we check the variable details of the Bangladesh birth history recode (BR) pooled dataset.

```{r}
#| label: dict-bdbr-pl
#| echo: false
#| output: true

# We create the data dictionary of the bdbr pooled dataset.
bdbr_pl |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdbr",
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

# Nepal DHS pooled data dictionary

Here we check the variable details of the Nepal birth history recode (BR) pooled dataset.

```{r}
#| label: dict-npbr-pl
#| echo: false
#| output: true

# We create the data dictionary of the npbr pooled dataset.
npbr_pl |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "npbr",
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```


