---
title: "Bangladesh DHS data dictionary"
---

# Getting started

Here we show the pre-requisite code sections. Run these at the outset to avoid errors. First we load the required packages.

```{r}
#| label: load-packages
#| echo: true
#| output: false

easypackages::libraries(
  # Data i/o
  "here",                 # relative file path
  "rio",                  # file import-export
  
  # Data manipulation
  "janitor",              # data cleaning fns
  "haven",                # stata, sas, spss data io
  "labelled",             # var labelling
  "readxl",               # excel sheets
  # "scales",               # to change formats and units
  "skimr",                # quick data summary
  "broom",                # view model results
  
  # Analysis output
  "gt",
  # "modelsummary",          # output summary tables
  "gtsummary",            # output summary tables
  "flextable",            # creating tables from objects
  "officer",              # editing in office docs
  
  # R graph related packages
  "ggstats",
  "RColorBrewer",
  # "scales",
  "patchwork",
  
  # Misc packages
  "tidyverse",            # Data manipulation iron man
  "tictoc"                # Code timing
)

```

Next we turn off scientific notations.

```{r}
#| label: turn-off-scientific-notation
#| echo: true
#| output: false

options(scipen = 999)

```

Next we set the default gtsummary print engine for tables.

```{r}
#| label: set-gtsummary-default
#| echo: true
#| output: false 

theme_gtsummary_printer(print_engine = "flextable")

```

Now we set the flextable output defaults.

```{r}
#| label: set-flextable-default
#| echo: true
#| output: false 

set_flextable_defaults(
  font.size = 11,
  text.align = "left",
  big.mark = "",
  background.color = "white",
  table.layout = "autofit",
  theme_fun = theme_vanilla
)

```

# Document introduction

We document the variable labels and other contents of all variables across all the Bangladesh Demographic and Health Survey (DHS) datasets here. This will be primary document for viewing what variables are available for use in PhD research. We check the variable labels before running the pooling code in "daprep-v01_bddhs.R".

This document contains variable details for the following Bangladesh DHS surveys:

```{r}
#| label: data-import
#| echo: false
#| output: false

# Here we temporarily import the tibbles for sample size table creation
# Importing the bdbr nested tibble
bdbr_raw <- read_rds(
  file = here("website_data", "bdbr1_nest0.rds")
)
# Importing the bdir nested tibble
bdir_raw <- read_rds(
  file = here("website_data", "bdir1_nest0.rds")
)
# Importing the bdhr nested tibble
bdhr_raw <- read_rds(
  file = here("website_data", "bdhr1_nest0.rds")
)
# Importing the bdpr nested tibble
bdpr_raw <- read_rds(
  file = here("website_data", "bdpr1_nest0.rds")
)

```

```{r}
#| label: tbl-detail-survey-rounds
#| echo: true
#| output: true
#| tbl-cap: "Bangladesh DHS datasets and their sample size to be used for pooling"

# Creating the table of surveys to be used for pooling
bdbr_raw |> 
  mutate(n_births = prettyNum(n_births, big.mark = ",")) |> 
  select(c(ctr_name, svy_year, n_births)) |> 
  # Join vars from bdir_tmp_intro
  left_join(
    bdir_raw |> 
      mutate(n_women = prettyNum(n_women, big.mark = ",")) |> 
      select(year, n_women),
    by = join_by(svy_year == year)
  ) |> 
  # Join vars from bdhr_tmp_intro
  left_join(
    bdhr_raw |> 
      mutate(n_households = prettyNum(n_households, big.mark = ",")) |> 
      select(svy_year, n_households),
    by = join_by(svy_year)
  ) |> 
  # Join vars from bdpr_tmp_intro
  left_join(
    bdpr_raw |> 
      mutate(n_persons = prettyNum(n_persons, big.mark = ",")) |> 
      select(svy_year, n_persons),
    by = join_by(svy_year)
  ) |> 
  # convert nested tibble to simple tibble
  unnest(cols = c()) |> 
  mutate(
    ccode = row_number(), 
    .before = ctr_name
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

Here we will create basic data dictionaries of each datasets using the labelled package. In our earlier efforts we realized that the method for generation data dictionaries for each dataset are similar. Hence, we will create a function using the look_for() command to generate the data dictionaries and view them.

```{r}
#| label: fn-gen-dadict
#| echo: false
#| output: false

# We create a function for generating basic data dictionary
dadict_basic <- function(df) {
  df |> 
  # create data dictionary
  labelled::lookfor(details = "basic") |> 
  # keep only the required columns
  select(-c(pos, levels, value_labels)) |> 
  # for correctly viewing the range column in data dictionary
  labelled::convert_list_columns_to_character()
}

```

# Bangladesh Birth History Recode data dictionary

Here we check the variable details of the Bangladesh birth history recode (BR) dataset. We will view the data dictionaries round-wise.

## Bangladesh BR 1993

Here we check the data dictionary of Bangladesh BR 1993 dataset.

```{r}
#| label: dict-bdbr-1993
#| echo: false
#| output: true

# We create the data dictionary of the bdbr 1993 dataset.
bdbr_raw$bdbr_data$bdbr_1993 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdbr",
    svy_year = 1993,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh BR 1996

Here we check the data dictionary of Bangladesh BR 1996 dataset.

```{r}
#| label: dict-bdbr-1996
#| echo: false
#| output: true

# We create the data dictionary of the bdbr 1996 dataset.
bdbr_raw$bdbr_data$bdbr_1996 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdbr",
    svy_year = 1996,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh BR 1999

Here we check the data dictionary of Bangladesh BR 1999 dataset.

```{r}
#| label: dict-bdbr-1999
#| echo: false
#| output: true

# We create the data dictionary of the bdbr 1999 dataset.
bdbr_raw$bdbr_data$bdbr_1999 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdbr",
    svy_year = 1999,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh BR 2004

Here we check the data dictionary of Bangladesh BR 2004 dataset.

```{r}
#| label: dict-bdbr-2004
#| echo: false
#| output: true

# We create the data dictionary of the bdbr 2004 dataset.
bdbr_raw$bdbr_data$bdbr_2004 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdbr",
    svy_year = 2004,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh BR 2007

Here we check the data dictionary of Bangladesh BR 2007 dataset.

```{r}
#| label: dict-bdbr-2007
#| echo: false
#| output: true

# We create the data dictionary of the bdbr 2007 dataset.
bdbr_raw$bdbr_data$bdbr_2007 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdbr",
    svy_year = 2007,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh BR 2011

Here we check the data dictionary of Bangladesh BR 2011 dataset.

```{r}
#| label: dict-bdbr-2011
#| echo: false
#| output: true

# We create the data dictionary of the bdbr 2011 dataset.
bdbr_raw$bdbr_data$bdbr_2011 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdbr",
    svy_year = 2011,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh BR 2014

Here we check the data dictionary of Bangladesh BR 2014 dataset.

```{r}
#| label: dict-bdbr-2014
#| echo: false
#| output: true

# We create the data dictionary of the bdbr 2014 dataset.
bdbr_raw$bdbr_data$bdbr_2014 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdbr",
    svy_year = 2014,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh BR 2017

Here we check the data dictionary of Bangladesh BR 2017 dataset.

```{r}
#| label: dict-bdbr-2017
#| echo: false
#| output: true

# We create the data dictionary of the bdbr 2017 dataset.
bdbr_raw$bdbr_data$bdbr_2017 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdbr",
    svy_year = 2017,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh BR 2022

Here we check the data dictionary of Bangladesh BR 2022 dataset.

```{r}
#| label: dict-bdbr-2022
#| echo: false
#| output: true

# We create the data dictionary of the bdbr 2022 dataset.
bdbr_raw$bdbr_data$bdbr_2022 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdbr",
    svy_year = 2022,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

# Bangladesh Individual Recode data dictionary

Here we check the variable details of the Bangladesh individual recode (IR) dataset. Note that, the individual recode files are generally huge in size. Therefore, we will import the original STATA datasets directly, prepare the data dictionaries and clear them from memory before proceeding with the next dataset. We will view the data dictionaries round-wise.

## Bangladesh IR 1993

Here we check the data dictionary of Bangladesh IR 1993 dataset.

```{r}
#| label: dict-bdir-1993
#| echo: false
#| output: true

# We create the data dictionary of the bdir 1993 dataset.
bdir_raw$bdir_data$bdir_1993 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdir",
    svy_year = 1993,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-bdir-1993
#| echo: false
#| output: false

# Remove data from memory
remove(bdir_1993)
# Clean unused memory
gc()

```

## Bangladesh IR 1996

Here we check the data dictionary of Bangladesh IR 1996 dataset.

```{r}
#| label: dict-bdir-1996
#| echo: false
#| output: true

# We create the data dictionary of the bdir 1996 dataset.
bdir_raw$bdir_data$bdir_1996 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdir",
    svy_year = 1996,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-bdir-1996
#| echo: false
#| output: false

# Remove data from memory
remove(bdir_1996)
# Clean unused memory
gc()

```

## Bangladesh IR 1999

Here we check the data dictionary of Bangladesh IR 1999 dataset.

```{r}
#| label: dict-bdir-1999
#| echo: false
#| output: true

# We create the data dictionary of the bdir 1999 dataset.
bdir_raw$bdir_data$bdir_1999 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdir",
    svy_year = 1999,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-bdir-1999
#| echo: false
#| output: false

# Remove data from memory
remove(bdir_1999)
# Clean unused memory
gc()

```

## Bangladesh IR 2004

Here we check the data dictionary of Bangladesh IR 2004 dataset.

```{r}
#| label: dict-bdir-2004
#| echo: false
#| output: true

# We create the data dictionary of the bdir 2004 dataset.
bdir_raw$bdir_data$bdir_2004 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdir",
    svy_year = 2004,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-bdir-2004
#| echo: false
#| output: false

# Remove data from memory
remove(bdir_2004)
# Clean unused memory
gc()

```

## Bangladesh IR 2007

Here we check the data dictionary of Bangladesh IR 2007 dataset.

```{r}
#| label: dict-bdir-2007
#| echo: false
#| output: true

# We create the data dictionary of the bdir 2007 dataset.
bdir_raw$bdir_data$bdir_2007 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdir",
    svy_year = 2007,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-bdir-2007
#| echo: false
#| output: false

# Remove data from memory
remove(bdir_2007)
# Clean unused memory
gc()

```

## Bangladesh IR 2011

Here we check the data dictionary of Bangladesh IR 2011 dataset.

```{r}
#| label: dict-bdir-2011
#| echo: false
#| output: true

# We create the data dictionary of the bdir 2011 dataset.
bdir_raw$bdir_data$bdir_2011 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdir",
    svy_year = 2011,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-bdir-2011
#| echo: false
#| output: false

# Remove data from memory
remove(bdir_2011)
# Clean unused memory
gc()

```

## Bangladesh IR 2014

Here we check the data dictionary of Bangladesh IR 2014 dataset.

```{r}
#| label: dict-bdir-2014
#| echo: false
#| output: true

# We create the data dictionary of the bdir 2014 dataset.
bdir_raw$bdir_data$bdir_2014 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdir",
    svy_year = 2014,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-bdir-2014
#| echo: false
#| output: false

# Remove data from memory
remove(bdir_2014)
# Clean unused memory
gc()

```

## Bangladesh IR 2017

Here we check the data dictionary of Bangladesh IR 2017 dataset.

```{r}
#| label: dict-bdir-2017
#| echo: false
#| output: true

# We create the data dictionary of the bdir 2017 dataset.
bdir_raw$bdir_data$bdir_2017 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdir",
    svy_year = 2017,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-bdir-2017
#| echo: false
#| output: false

# Remove data from memory
remove(bdir_2017)
# Clean unused memory
gc()

```

## Bangladesh IR 2022

Here we check the data dictionary of Bangladesh IR 2022 dataset.

```{r}
#| label: dict-bdir-2022
#| echo: false
#| output: true

# We create the data dictionary of the bdir 2022 dataset.
bdir_raw$bdir_data$bdir_2022 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdir",
    svy_year = 2022,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-bdir-2022
#| echo: false
#| output: false

# Remove data from memory
remove(bdir_2022)
# Clean unused memory
gc()

```

# Bangladesh Household Recode data dictionary

Here we check the variable details of the Bangladesh household recode (HR) dataset. We will view the data dictionaries round-wise.

## Bangladesh HR 1993

Here we check the data dictionary of Bangladesh HR 1993 dataset.

```{r}
#| label: dict-bdhr-1993
#| echo: false
#| output: true

# We create the data dictionary of the bdhr 1993 dataset.
bdhr_raw$bdhr_data$bdhr_1993 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdhr",
    svy_year = 1993,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh HR 1996

Here we check the data dictionary of Bangladesh HR 1996 dataset.

```{r}
#| label: dict-bdhr-1996
#| echo: false
#| output: true

# We create the data dictionary of the bdhr 1996 dataset.
bdhr_raw$bdhr_data$bdhr_1996 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdhr",
    svy_year = 1996,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh HR 1999

Here we check the data dictionary of Bangladesh HR 1999 dataset.

```{r}
#| label: dict-bdhr-1999
#| echo: false
#| output: true

# We create the data dictionary of the bdhr 1999 dataset.
bdhr_raw$bdhr_data$bdhr_1999 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdhr",
    svy_year = 1999,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh HR 2004

Here we check the data dictionary of Bangladesh HR 2004 dataset.

```{r}
#| label: dict-bdhr-2004
#| echo: false
#| output: true

# We create the data dictionary of the bdhr 2004 dataset.
bdhr_raw$bdhr_data$bdhr_2004 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdhr",
    svy_year = 2004,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh HR 2007

Here we check the data dictionary of Bangladesh HR 2007 dataset.

```{r}
#| label: dict-bdhr-2007
#| echo: false
#| output: true

# We create the data dictionary of the bdhr 2007 dataset.
bdhr_raw$bdhr_data$bdhr_2007 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdhr",
    svy_year = 2007,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh HR 2011

Here we check the data dictionary of Bangladesh HR 2011 dataset.

```{r}
#| label: dict-bdhr-2011
#| echo: false
#| output: true

# We create the data dictionary of the bdhr 2011 dataset.
bdhr_raw$bdhr_data$bdhr_2011 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdhr",
    svy_year = 2011,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh HR 2014

Here we check the data dictionary of Bangladesh HR 2014 dataset.

```{r}
#| label: dict-bdhr-2014
#| echo: false
#| output: true

# We create the data dictionary of the bdhr 2014 dataset.
bdhr_raw$bdhr_data$bdhr_2014 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdhr",
    svy_year = 2014,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh HR 2017

Here we check the data dictionary of Bangladesh HR 2017 dataset.

```{r}
#| label: dict-bdhr-2017
#| echo: false
#| output: true

# We create the data dictionary of the bdhr 2017 dataset.
bdhr_raw$bdhr_data$bdhr_2017 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdhr",
    svy_year = 2017,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh HR 2022

Here we check the data dictionary of Bangladesh HR 2022 dataset.

```{r}
#| label: dict-bdhr-2022
#| echo: false
#| output: true

# We create the data dictionary of the bdhr 2022 dataset.
bdhr_raw$bdhr_data$bdhr_2022 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdhr",
    svy_year = 2022,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

# Bangladesh Person Recode data dictionary

Here we check the variable details of the Bangladesh person recode (PR) dataset. We will view the data dictionaries round-wise.

## Bangladesh PR 1993

Here we check the data dictionary of Bangladesh PR 1993 dataset.

```{r}
#| label: dict-bdpr-1993
#| echo: false
#| output: true

# We create the data dictionary of the bdpr 1993 dataset.
bdpr_raw$bdpr_data$bdpr_1993 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdpr",
    svy_year = 1993,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh PR 1996

Here we check the data dictionary of Bangladesh PR 1996 dataset.

```{r}
#| label: dict-bdpr-1996
#| echo: false
#| output: true

# We create the data dictionary of the bdpr 1996 dataset.
bdpr_raw$bdpr_data$bdpr_1996 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdpr",
    svy_year = 1996,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh PR 1999

Here we check the data dictionary of Bangladesh PR 1999 dataset.

```{r}
#| label: dict-bdpr-1999
#| echo: false
#| output: true

# We create the data dictionary of the bdpr 1999 dataset.
bdpr_raw$bdpr_data$bdpr_1999 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdpr",
    svy_year = 1999,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh PR 2004

Here we check the data dictionary of Bangladesh PR 2004 dataset.

```{r}
#| label: dict-bdpr-2004
#| echo: false
#| output: true

# We create the data dictionary of the bdpr 2004 dataset.
bdpr_raw$bdpr_data$bdpr_2004 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdpr",
    svy_year = 2004,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh PR 2007

Here we check the data dictionary of Bangladesh PR 2007 dataset.

```{r}
#| label: dict-bdpr-2007
#| echo: false
#| output: true

# We create the data dictionary of the bdpr 2007 dataset.
bdpr_raw$bdpr_data$bdpr_2007 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdpr",
    svy_year = 2007,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh PR 2011

Here we check the data dictionary of Bangladesh PR 2011 dataset.

```{r}
#| label: dict-bdpr-2011
#| echo: false
#| output: true

# We create the data dictionary of the bdpr 2011 dataset.
bdpr_raw$bdpr_data$bdpr_2011 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdpr",
    svy_year = 2011,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh PR 2014

Here we check the data dictionary of Bangladesh PR 2014 dataset.

```{r}
#| label: dict-bdpr-2014
#| echo: false
#| output: true

# We create the data dictionary of the bdpr 2014 dataset.
bdpr_raw$bdpr_data$bdpr_2014 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdpr",
    svy_year = 2014,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh PR 2017

Here we check the data dictionary of Bangladesh PR 2017 dataset.

```{r}
#| label: dict-bdpr-2017
#| echo: false
#| output: true

# We create the data dictionary of the bdpr 2017 dataset.
bdpr_raw$bdpr_data$bdpr_2017 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdpr",
    svy_year = 2017,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Bangladesh PR 2022

Here we check the data dictionary of Bangladesh PR 2022 dataset.

```{r}
#| label: dict-bdpr-2022
#| echo: false
#| output: true

# We create the data dictionary of the bdpr 2022 dataset.
bdpr_raw$bdpr_data$bdpr_2022 |>
  # generate data dictionary
  dadict_basic() |> 
  # include survey name and year for reference
  mutate(
    svy_name = "bdpr",
    svy_year = 2022,
    .before = 1
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```




