---
title: "Pakistan DHS data dictionary"
---

# Getting started

First we load the required packages.

```{r}
#| label: load-packages
#| echo: true
#| output: false

easypackages::libraries(
  # Data i/o
  "here",                 # relative file path
  "rio",                  # file import-export
  
  # Data manipulation
  "janitor",              # data cleaning fns
  "haven",                # stata, sas, spss data io
  "labelled",             # var labelling
  "readxl",               # excel sheets
  # "scales",               # to change formats and units
  "skimr",                # quick data summary
  "hroom",                # view model results
  
  # Analysis output
  "gt",
  # "modelsummary",          # output summary tables
  "gtsummary",            # output summary tables
  "flextable",            # creating tables from objects
  "officer",              # editing in office docs
  
  # R graph related packages
  "ggstats",
  "RColorBrewer",
  # "scales",
  "patchwork",
  
  # Misc packages
  "tidyverse",            # Data manipulation iron man
  "tictoc"                # Code timing
)

```

Next we turn off scientific notations.

```{r}
#| label: turn-off-scientific-notation
#| echo: true
#| output: false

options(scipen = 999)

```

Next we set the default gtsummary print engine for tables.

```{r}
#| label: set-gtsummary-default
#| echo: true
#| output: false 

theme_gtsummary_printer(print_engine = "flextable")

```

Now we set the flextable output defaults.

```{r}
#| label: set-flextable-default
#| echo: true
#| output: false 

set_flextable_defaults(
  font.size = 10, 
  # font.family = "Helvetica",
  theme_fun = theme_vanilla
)

```

# Document introduction

We document the variable labels and other contents of all variables across all the Pakistan Demographic and Health Survey (DHS) datasets here. This will be primary document for viewing what variables are available for use in PhD research. We check the variable labels before running the pooling code in "daprep-v01_pkdhs.R". 

This document contains variable details for the following Pakistan DHS surveys:

```{r}
#| label: data-import
#| echo: false
#| output: false

# Here we temporarily import the tibbles for sample size table creation
# Importing the pkbr nested tibble
pkbr_raw <- read_rds(
  file = here("website_data", "pkbr1_nest0.rds")
)
# Importing the pkir nested tibble
pkir_raw <- read_rds(
  file = here("website_data", "pkir1_nest0.rds")
)
# Importing the pkhr nested tibble
pkhr_raw <- read_rds(
  file = here("website_data", "pkhr1_nest0.rds")
)
# Importing the pkpr nested tibble
pkpr_raw <- read_rds(
  file = here("website_data", "pkpr1_nest0.rds")
)

```

```{r}
#| label: tbl-detail-survey-rounds
#| echo: true
#| output: true
#| tbl-cap: "Pakistan DHS datasets and their sample size to be used for pooling"

# Creating the table of surveys to be used for pooling
pkbr_raw |> select(c(ctr_name, svy_year, n_births)) |> 
  # Join vars from pkhr_tmp_intro
  left_join(
    pkhr_raw |> select(svy_year, n_households),
    by = join_by(svy_year)
  ) |> 
  # Join vars from pkpr_tmp_intro
  left_join(
    pkpr_raw |> select(svy_year, n_persons),
    by = join_by(svy_year)
  ) |> 
  # convert nested tibble to simple tibble
  unnest(cols = c()) |> 
  mutate(
    ccode = row_number(), 
    .before = ctr_name
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all") |> 
  autofit()

```

Here we will create basic data dictionaries of each datasets using the labelled package. In our earlier efforts we realized that the method for generation data dictionaries for each dataset are similar. Hence, we will create a function using the look_for() command to generate the data dictionaries and view them.

```{r}
#| label: fn-gen-dadict
#| echo: false
#| output: false

# We create a function for generating basic data dictionary
dadict_basic <- function(df) {
  df |> 
  # create data dictionary
  labelled::lookfor(details = "basic") |> 
  # keep only the required columns
  select(-c(levels, value_labels)) |> 
  # for correctly viewing the range column in data dictionary
  labelled::convert_list_columns_to_character()
}

```

# Pakistan Birth History Recode data dictionary

Here we check the variable details of the Pakistan birth history recode (BR) dataset. We will view the data dictionaries round-wise.

## Pakistan BR 1990

Here we check the data dictionary of Pakistan BR 1990 dataset.

```{r}
#| label: dict-pkbr-1990
#| echo: false
#| output: true

# We create the data dictionary of the pkbr 1990 dataset.
pkbr_raw$pkbr_data$pkbr_1990 |>
  # generate basic data dictionary 
  dadict_basic() |>  
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Pakistan BR 2006

Here we check the data dictionary of Pakistan BR 2006 dataset.

```{r}
#| label: dict-pkbr-2006
#| echo: false
#| output: true

# We create the data dictionary of the pkbr 2006 dataset.
pkbr_raw$pkbr_data$pkbr_2006 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Pakistan BR 2012

Here we check the data dictionary of Pakistan BR 2012 dataset.

```{r}
#| label: dict-pkbr-2012
#| echo: false
#| output: true

# We create the data dictionary of the pkbr 2012 dataset.
pkbr_raw$pkbr_data$pkbr_2012 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Pakistan BR 2017

Here we check the data dictionary of Pakistan BR 2017 dataset.

```{r}
#| label: dict-pkbr-2017
#| echo: false
#| output: true

# We create the data dictionary of the pkbr 2017 dataset.
pkbr_raw$pkbr_data$pkbr_2017 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

# Pakistan Individual Recode data dictionary

Here we check the variable details of the Pakistan individual recode (IR) dataset. Note that, the individual recode files are generally huge in size. Therefore, we will import the original STATA datasets directly, prepare the data dictionaries and clear them from memory before proceeding with the next dataset. We will view the data dictionaries round-wise.

## Pakistan IR 1990

Here we check the data dictionary of Pakistan IR 1990 dataset.

```{r}
#| label: dict-pkir-1990
#| echo: false
#| output: true

# We create the data dictionary of the pkir 1990 dataset.
pkir_raw$pkir_data$pkir_1990 |>
  # generate basic data dictionary 
  dadict_basic() |>  
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-pkir-1990
#| echo: false
#| output: false

# Remove data from memory
remove(pkir_1990)
# Clean unused memory
gc()

```

## Pakistan IR 2006

Here we check the data dictionary of Pakistan IR 2006 dataset.

```{r}
#| label: dict-pkir-2006
#| echo: false
#| output: true

# We create the data dictionary of the pkir 2006 dataset.
pkir_raw$pkir_data$pkir_2006 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-pkir-2006
#| echo: false
#| output: false

# Remove data from memory
remove(pkir_2006)
# Clean unused memory
gc()

```

## Pakistan IR 2012

Here we check the data dictionary of Pakistan IR 2012 dataset.

```{r}
#| label: dict-pkir-2012
#| echo: false
#| output: true

# We create the data dictionary of the pkir 2012 dataset.
pkir_raw$pkir_data$pkir_2012 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-pkir-2012
#| echo: false
#| output: false

# Remove data from memory
remove(pkir_2012)
# Clean unused memory
gc()

```

## Pakistan IR 2017

Here we check the data dictionary of Pakistan IR 2017 dataset.

```{r}
#| label: dict-pkir-2017
#| echo: false
#| output: true

# We create the data dictionary of the pkir 2017 dataset.
pkir_raw$pkir_data$pkir_2017 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-pkir-2017
#| echo: false
#| output: false

# Remove data from memory
remove(pkir_2017)
# Clean unused memory
gc()

```

# Pakistan Household Recode data dictionary

Here we check the variable details of the Pakistan household recode (HR) dataset. We will view the data dictionaries round-wise.

## Pakistan HR 1990

Here we check the data dictionary of Pakistan HR 1990 dataset.

```{r}
#| label: dict-pkhr-1990
#| echo: false
#| output: true

# We create the data dictionary of the pkhr 1990 dataset.
pkhr_raw$pkhr_data$pkhr_1990 |>
  # generate basic data dictionary 
  dadict_basic() |>  
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Pakistan HR 2006

Here we check the data dictionary of Pakistan HR 2006 dataset.

```{r}
#| label: dict-pkhr-2006
#| echo: false
#| output: true

# We create the data dictionary of the pkhr 2006 dataset.
pkhr_raw$pkhr_data$pkhr_2006 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Pakistan HR 2012

Here we check the data dictionary of Pakistan HR 2012 dataset.

```{r}
#| label: dict-pkhr-2012
#| echo: false
#| output: true

# We create the data dictionary of the pkhr 2012 dataset.
pkhr_raw$pkhr_data$pkhr_2012 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Pakistan HR 2017

Here we check the data dictionary of Pakistan HR 2017 dataset.

```{r}
#| label: dict-pkhr-2017
#| echo: false
#| output: true

# We create the data dictionary of the pkhr 2017 dataset.
pkhr_raw$pkhr_data$pkhr_2017 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

# Pakistan Person Recode data dictionary

Here we check the variable details of the Pakistan person recode (PR) dataset. We will view the data dictionaries round-wise.

## Pakistan PR 1990

Here we check the data dictionary of Pakistan PR 1990 dataset.

```{r}
#| label: dict-pkpr-1990
#| echo: false
#| output: true

# We create the data dictionary of the pkpr 1990 dataset.
pkpr_raw$pkpr_data$pkpr_1990 |>
  # generate basic data dictionary 
  dadict_basic() |>  
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Pakistan PR 2006

Here we check the data dictionary of Pakistan PR 2006 dataset.

```{r}
#| label: dict-pkpr-2006
#| echo: false
#| output: true

# We create the data dictionary of the pkpr 2006 dataset.
pkpr_raw$pkpr_data$pkpr_2006 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Pakistan PR 2012

Here we check the data dictionary of Pakistan PR 2012 dataset.

```{r}
#| label: dict-pkpr-2012
#| echo: false
#| output: true

# We create the data dictionary of the pkpr 2012 dataset.
pkpr_raw$pkpr_data$pkpr_2012 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Pakistan PR 2017

Here we check the data dictionary of Pakistan PR 2017 dataset.

```{r}
#| label: dict-pkpr-2017
#| echo: false
#| output: true

# We create the data dictionary of the pkpr 2017 dataset.
pkpr_raw$pkpr_data$pkpr_2017 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```









