---
title: "Nepal DHS data dictionary"
---

# Getting started

First we load the required packages.

```{r}
#| label: load-packages
#| echo: true
#| output: false

easypackages::libraries(
  # Data i/o
  "here",                 # relative file path
  "rio",                  # file import-export
  
  # Data manipulation
  "janitor",              # data cleaning fns
  "haven",                # stata, sas, spss data io
  "labelled",             # var labelling
  "readxl",               # excel sheets
  # "scales",               # to change formats and units
  "skimr",                # quick data summary
  "broom",                # view model results
  
  # Analysis output
  "gt",
  # "modelsummary",          # output summary tables
  "gtsummary",            # output summary tables
  "flextable",            # creating tables from objects
  "officer",              # editing in office docs
  
  # R graph related packages
  "ggstats",
  "RColorBrewer",
  # "scales",
  "patchwork",
  
  # Misc packages
  "tidyverse",            # Data manipulation iron man
  "tictoc"                # Code timing
)

```

Next we turn off scientific notations.

```{r}
#| label: turn-off-scientific-notation
#| echo: true
#| output: false

options(scipen = 999)

```

Next we set the default gtsummary print engine for tables.

```{r}
#| label: set-gtsummary-default
#| echo: true
#| output: false 

theme_gtsummary_printer(print_engine = "flextable")

```

Now we set the flextable output defaults.

```{r}
#| label: set-flextable-default
#| echo: true
#| output: false 

set_flextable_defaults(
  font.size = 10, 
  # font.family = "Helvetica",
  theme_fun = theme_vanilla
)

```

# Document introduction

We document the variable labels and other contents of all variables across all the Nepal Demographic and Health Survey (DHS) datasets here. This will be primary document for viewing what variables are available for use in PhD research. We check the variable labels before running the pooling code in "daprep-v01_npdhs.R". 

This document contains variable details for the following Nepal DHS surveys:

```{r}
#| label: data-import
#| echo: false
#| output: false

# Here we temporarily import the tibbles for sample size table creation
# Importing the npbr nested tibble
npbr_raw <- read_rds(
  file = here("website_data", "npbr1_nest0.rds")
)
# Importing the npir nested tibble
npir_raw <- read_rds(
  file = here("website_data", "npir1_nest0.rds")
)
# Importing the nphr nested tibble
nphr_raw <- read_rds(
  file = here("website_data", "nphr1_nest0.rds")
)
# Importing the nppr nested tibble
nppr_raw <- read_rds(
  file = here("website_data", "nppr1_nest0.rds")
)

```

```{r}
#| label: tbl-detail-survey-rounds
#| echo: true
#| output: true
#| tbl-cap: "Nepal DHS datasets and their sample size to be used for pooling"

# Creating the table of surveys to be used for pooling
npbr_raw |> select(c(ctr_name, svy_year, n_births)) |> 
  # Join vars from nphr_tmp_intro
  left_join(
    nphr_raw |> select(svy_year, n_households),
    by = join_by(svy_year)
  ) |> 
  # Join vars from nppr_tmp_intro
  left_join(
    nppr_raw |> select(svy_year, n_persons),
    by = join_by(svy_year)
  ) |> 
  # convert nested tibble to simple tibble
  unnest(cols = c()) |> 
  mutate(
    ccode = row_number(), 
    .before = ctr_name
  ) |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all") |> 
  autofit()

```

Here we will create basic data dictionaries of each datasets using the labelled package. In our earlier efforts we realized that the method for generation data dictionaries for each dataset are similar. Hence, we will create a function using the look_for() command to generate the data dictionaries and view them.

```{r}
#| label: fn-gen-dadict
#| echo: false
#| output: false

# We create a function for generating basic data dictionary
dadict_basic <- function(df) {
  df |> 
  # create data dictionary
  labelled::lookfor(details = "basic") |> 
  # keep only the required columns
  select(-c(levels, value_labels)) |> 
  # for correctly viewing the range column in data dictionary
  labelled::convert_list_columns_to_character()
}

```

# Nepal Birth History Recode data dictionary

Here we check the variable details of the Nepal birth history recode (BR) dataset. We will view the data dictionaries round-wise.

## Nepal BR 1996

Here we check the data dictionary of Nepal BR 1996 dataset.

```{r}
#| label: dict-npbr-1996
#| echo: false
#| output: true

# We create the data dictionary of the npbr 1996 dataset.
npbr_raw$npbr_data$npbr_1996 |>
  # generate basic data dictionary 
  dadict_basic() |>  
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal BR 2001

Here we check the data dictionary of Nepal BR 2001 dataset.

```{r}
#| label: dict-npbr-2001
#| echo: false
#| output: true

# We create the data dictionary of the npbr 2001 dataset.
npbr_raw$npbr_data$npbr_2001 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal BR 2006

Here we check the data dictionary of Nepal BR 2006 dataset.

```{r}
#| label: dict-npbr-2006
#| echo: false
#| output: true

# We create the data dictionary of the npbr 2006 dataset.
npbr_raw$npbr_data$npbr_2006 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal BR 2011

Here we check the data dictionary of Nepal BR 2011 dataset.

```{r}
#| label: dict-npbr-2011
#| echo: false
#| output: true

# We create the data dictionary of the npbr 2011 dataset.
npbr_raw$npbr_data$npbr_2011 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal BR 2016

Here we check the data dictionary of Nepal BR 2016 dataset.

```{r}
#| label: dict-npbr-2016
#| echo: false
#| output: true

# We create the data dictionary of the npbr 2016 dataset.
npbr_raw$npbr_data$npbr_2016 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal BR 2022

Here we check the data dictionary of Nepal BR 2022 dataset.

```{r}
#| label: dict-npbr-2022
#| echo: false
#| output: true

# We create the data dictionary of the npbr 2022 dataset.
npbr_raw$npbr_data$npbr_2022 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

# Nepal Individual Recode data dictionary

Here we check the variable details of the Nepal individual recode (IR) dataset. Note that, the individual recode files are generally huge in size. Therefore, we will import the original STATA datasets directly, prepare the data dictionaries and clear them from memory before proceeding with the next dataset. We will view the data dictionaries round-wise.

## Nepal IR 1996

Here we check the data dictionary of Nepal IR 1996 dataset.

```{r}
#| label: dict-npir-1996
#| echo: false
#| output: true

# We create the data dictionary of the npir 1996 dataset.
npir_raw$npir_data$npir_1996 |>
  # generate basic data dictionary 
  dadict_basic() |>  
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-npir-1996
#| echo: false
#| output: false

# Remove data from memory
remove(npir_1996)
# Clean unused memory
gc()

```

## Nepal IR 2001

Here we check the data dictionary of Nepal IR 2001 dataset.

```{r}
#| label: dict-npir-2001
#| echo: false
#| output: true

# We create the data dictionary of the npir 2001 dataset.
npir_raw$npir_data$npir_2001 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-npir-2001
#| echo: false
#| output: false

# Remove data from memory
remove(npir_2001)
# Clean unused memory
gc()

```

## Nepal IR 2006

Here we check the data dictionary of Nepal IR 2006 dataset.

```{r}
#| label: dict-npir-2006
#| echo: false
#| output: true

# We create the data dictionary of the npir 2006 dataset.
npir_raw$npir_data$npir_2006 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-npir-2006
#| echo: false
#| output: false

# Remove data from memory
remove(npir_2006)
# Clean unused memory
gc()

```

## Nepal IR 2011

Here we check the data dictionary of Nepal IR 2011 dataset.

```{r}
#| label: dict-npir-2011
#| echo: false
#| output: true

# We create the data dictionary of the npir 2011 dataset.
npir_raw$npir_data$npir_2011 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-npir-2011
#| echo: false
#| output: false

# Remove data from memory
remove(npir_2011)
# Clean unused memory
gc()

```

## Nepal IR 2016

Here we check the data dictionary of Nepal IR 2016 dataset.

```{r}
#| label: dict-npir-2016
#| echo: false
#| output: true

# We create the data dictionary of the npir 2016 dataset.
npir_raw$npir_data$npir_2016 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-npir-2016
#| echo: false
#| output: false

# Remove data from memory
remove(npir_2016)
# Clean unused memory
gc()

```

## Nepal IR 2022

Here we check the data dictionary of Nepal IR 2022 dataset.

```{r}
#| label: dict-npir-2022
#| echo: false
#| output: true

# We create the data dictionary of the npir 2022 dataset.
npir_raw$npir_data$npir_2022 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

```{r}
#| label: remove-npir-2022
#| echo: false
#| output: false

# Remove data from memory
remove(npir_2022)
# Clean unused memory
gc()

```

# Nepal Household Recode data dictionary

Here we check the variable details of the Nepal household recode (HR) dataset. We will view the data dictionaries round-wise.

## Nepal HR 1996

Here we check the data dictionary of Nepal HR 1996 dataset.

```{r}
#| label: dict-nphr-1996
#| echo: false
#| output: true

# We create the data dictionary of the nphr 1996 dataset.
nphr_raw$nphr_data$nphr_1996 |>
  # generate basic data dictionary 
  dadict_basic() |>  
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal HR 2001

Here we check the data dictionary of Nepal HR 2001 dataset.

```{r}
#| label: dict-nphr-2001
#| echo: false
#| output: true

# We create the data dictionary of the nphr 2001 dataset.
nphr_raw$nphr_data$nphr_2001 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal HR 2006

Here we check the data dictionary of Nepal HR 2006 dataset.

```{r}
#| label: dict-nphr-2006
#| echo: false
#| output: true

# We create the data dictionary of the nphr 2006 dataset.
nphr_raw$nphr_data$nphr_2006 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal HR 2011

Here we check the data dictionary of Nepal HR 2011 dataset.

```{r}
#| label: dict-nphr-2011
#| echo: false
#| output: true

# We create the data dictionary of the nphr 2011 dataset.
nphr_raw$nphr_data$nphr_2011 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal HR 2016

Here we check the data dictionary of Nepal HR 2016 dataset.

```{r}
#| label: dict-nphr-2016
#| echo: false
#| output: true

# We create the data dictionary of the nphr 2016 dataset.
nphr_raw$nphr_data$nphr_2016 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal HR 2022

Here we check the data dictionary of Nepal HR 2022 dataset.

```{r}
#| label: dict-nphr-2022
#| echo: false
#| output: true

# We create the data dictionary of the nphr 2022 dataset.
nphr_raw$nphr_data$nphr_2022 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

# Nepal Person Recode data dictionary

Here we check the variable details of the Nepal person recode (PR) dataset. We will view the data dictionaries round-wise.

## Nepal PR 1996

Here we check the data dictionary of Nepal PR 1996 dataset.

```{r}
#| label: dict-nppr-1996
#| echo: false
#| output: true

# We create the data dictionary of the nppr 1996 dataset.
nppr_raw$nppr_data$nppr_1996 |>
  # generate basic data dictionary 
  dadict_basic() |>  
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal PR 2001

Here we check the data dictionary of Nepal PR 2001 dataset.

```{r}
#| label: dict-nppr-2001
#| echo: false
#| output: true

# We create the data dictionary of the nppr 2001 dataset.
nppr_raw$nppr_data$nppr_2001 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal PR 2006

Here we check the data dictionary of Nepal PR 2006 dataset.

```{r}
#| label: dict-nppr-2006
#| echo: false
#| output: true

# We create the data dictionary of the nppr 2006 dataset.
nppr_raw$nppr_data$nppr_2006 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal PR 2011

Here we check the data dictionary of Nepal PR 2011 dataset.

```{r}
#| label: dict-nppr-2011
#| echo: false
#| output: true

# We create the data dictionary of the nppr 2011 dataset.
nppr_raw$nppr_data$nppr_2011 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal PR 2016

Here we check the data dictionary of Nepal PR 2016 dataset.

```{r}
#| label: dict-nppr-2016
#| echo: false
#| output: true

# We create the data dictionary of the nppr 2016 dataset.
nppr_raw$nppr_data$nppr_2016 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```

## Nepal PR 2022

Here we check the data dictionary of Nepal PR 2022 dataset.

```{r}
#| label: dict-nppr-2022
#| echo: false
#| output: true

# We create the data dictionary of the nppr 2022 dataset.
nppr_raw$nppr_data$nppr_2022 |>
  # generate basic data dictionary 
  dadict_basic() |> 
  # convert to flextable object
  qflextable() |> 
  align(align = "left", part = "all")

```










