---
title: "South Asia DHS variable checklist"
---

# Getting started

Here we show the pre-requisite code sections. Run these at the outset to avoid errors. First we load the required packages.

```{r}
#| label: load-packages
#| echo: true
#| output: false

easypackages::libraries(
  # Data i/o
  "here",                 # relative file path
  "rio",                  # file import-export
  
  # Data manipulation
  "janitor",              # data cleaning fns
  "haven",                # stata, sas, spss data io
  "labelled",             # var labelling
  "readxl",               # excel sheets
  # "scales",               # to change formats and units
  "skimr",                # quick data summary
  "broom",                # view model results
  
  # Analysis output
  "gt",
  # "modelsummary",          # output summary tables
  "gtsummary",            # output summary tables
  "flextable",            # creating tables from objects
  "officer",              # editing in office docs
  
  # R graph related packages
  "ggstats",
  "RColorBrewer",
  # "scales",
  "patchwork",
  
  # Misc packages
  "tidyverse",            # Data manipulation iron man
  "tictoc"                # Code timing
)

```

Next we turn off scientific notations.

```{r}
#| label: turn-off-scientific-notation
#| echo: true
#| output: false

options(scipen = 999)

```

Next we set the default gtsummary print engine for tables.

```{r}
#| label: set-gtsummary-default
#| echo: true
#| output: false 

theme_gtsummary_printer(print_engine = "flextable")

```

Now we set the flextable output defaults.

```{r}
#| label: set-flextable-default
#| echo: true
#| output: false 

set_flextable_defaults(
  font.size = 11,
  text.align = "left",
  big.mark = "",
  background.color = "white",
  table.layout = "autofit",
  theme_fun = theme_vanilla
)

```

# Introduction

On this page we show the variable checklist of South Asian Demographic and Health Survey (DHS) datasets. This will be the primary document for viewing what variables are available for use in the DHS datasets in South Asia and across the countries. We check the variable availability from the raw data dictionaries and after that run the data pooling code. 

Across all the checklists, we have dataset name in the table header row, variable label in the table col and variable name as records. If a variable is available in the dataset we give the variable name and if it's unavailable we keep the records as missing.

# Afghanistan variable checklist

The variable availability for Afghanistan is given below.

```{r}
#| label: data-checklist-af
#| echo: false
#| output: false

# We create the data of the AFDHS dataset
afdhs <- tribble(
    ~var_name, ~af_2015,
    "ID and Weight variables",          NA,
    "Women's ind sample weight",        "v005",
    "Primary sampling unit",            "v021",
    "Sample stratum number",            "v022",
    "Strata used in sample design",     "v023",
    "Cluster number",                   "v001",
    "Household number",                 "v002",
    "Respondent's line number",         "v003",
    "Birth order",                      "bord",
    "Sub-national region vars",         NA,
    "Region/Division",                  "v024",
    "District of residence",            "sdistrict",
    "Ecological region",                NA,
    "Birth history variables",          NA,
    "Survival status of child",         "b5",
    "Child's age at death (cmc)",       "b7",
    "Child is twin",                    "b0",
    "Child's month of birth",           "b1",
    "Child's year of birth",            "b2",
    "Child's date of birth (cmc)",      "b3",
    "Child's sex",                      "b4",
    "Preceding birth interval",         "b11",
    "Mother-level variables",           NA,
    "Mother's date of birth (cmc)",     "v011",
    "Highest education level",          "v106",
    "Current marital status",           "v501",
    "Partner's education level",        "v701",
    "Mother's anemia level",            NA,
    "Respondent's weight in kg",        NA,
    "Respondent's height in cm",        NA,
    "Household-level variables",        NA,
    "Sex of household head",            "v151",
    "Age of household head",            "v152",
    "Wealth index quintile",            "v190",
    "Social group variables",           NA,
    "Religion",                         NA,
    "Caste",                            NA,
    "Ethnicity",                        "v131",
    "Language of questionnaire",        NA,
    "Language of interview",            "v045b",
    "Native language of respondent",    "v045c",
    "Family-structure variables",       NA,
    "Relationship to hh head",          "hv101",
    "De jure residents",                "hv102",
    "De facto residents",               "hv103",
    "Sex of hh member",                 "hv104",
    "Age of hh member",                 "hv105",
    "Highest education of hh member",   "hv106",
    "Community-level variables",        NA,
    "Distance to healthcare facility",  "v467",
    "Covered by health insurance",      "v481",
    "Cluster altitude",                 NA
) |> 
  mutate(pos = row_number(), .before = 1)

```

```{r}
#| label: tbl-checklist-af
#| echo: false
#| output: true
#| tbl-cap: "Checklist of variables in Afghanistan DHS"

# We create the flextable of the AFDHS dataset
afdhs |> 
  flextable() |> 
  set_header_labels(
    var_name = "Variable labels",
    af_2015 = "AFDHS 2015"
  ) |> 
  # make section headers bold-italicized
  bold(i = c(1, 10, 14, 23, 31, 35, 42, 49), part = "body") |> 
  italic(i = c(1, 10, 14, 23, 31, 35, 42, 49), part = "body") |> 
  # apply green background to rows with non-missing values
  bg(i = ~ !is.na(af_2015), j = 3:(ncol(afdhs)), bg = "lightgreen")
  
```

# Bangladesh variable checklist

The variable availability for Bangladesh is given below.

```{r}
#| label: data-checklist-bd
#| echo: false
#| output: false

# We create the data of the BDDHS dataset
bddhs <- tribble(
    ~var_name, ~bd_1993, ~bd_1996, ~bd_1999, ~bd_2004, ~bd_2007, ~bd_2011, ~bd_2014, ~bd_2017, ~bd_2022,
    "ID and Weight variables",          NA, NA, NA, NA, NA, NA, NA, NA, NA,
    "Women's ind sample weight",        "v005", "v005", "v005", "v005", "v005", "v005", "v005", "v005", "v005", 
    "Primary sampling unit",            "v021", "v021", "v021", "v021", "v021", "v021", "v021", "v021", "v021", 
    "Sample stratum number",            "v022", "v022", "v022", "v022", "v022", "v022", "v022", "v022", "v022", 
    "Strata used in sample design",     "v023", "v023", "v023", "v023", "v023", "v023", "v023", "v023", "v023", 
    "Cluster number",                   "v001", "v001", "v001", "v001", "v001", "v001", "v001", "v001", "v001", 
    "Household number",                 "v002", "v002", "v002", "v002", "v002", "v002", "v002", "v002", "v002", 
    "Respondent's line number",         "v003", "v003", "v003", "v003", "v003", "v003", "v003", "v003", "v003", 
    "Birth order",                      "bord", "bord", "bord", "bord", "bord", "bord", "bord", "bord", "bord", 
    "Sub-national region vars",         NA, NA, NA, NA, NA, NA, NA, NA, NA, 
    "Region/Division",                  "v024", "v024", "v024", "v024", "v024", "v024", "v024", "v024", "v024", 
    "District of residence",            "sdistrict", "sdistrict", "sdistrict", "sdistrict", "sdistrict", "sdistrict", "sdistrict", "sdistrict", "sdistrict", 
    "Ecological region",                NA, NA, NA, NA, NA, NA, NA, NA, NA, 
    "Birth history variables",          NA, NA, NA, NA, NA, NA, NA, NA, NA, 
    "Survival status of child",         "b5", "b5", "b5", "b5", "b5", "b5", "b5", "b5", "b5", 
    "Child's age at death (cmc)",       "b7", "b7", "b7", "b7", "b7", "b7", "b7", "b7", "b7", 
    "Child is twin",                    "b0", "b0", "b0", "b0", "b0", "b0", "b0", "b0", "b0", 
    "Child's month of birth",           "b1", "b1", "b1", "b1", "b1", "b1", "b1", "b1", "b1", 
    "Child's year of birth",            "b2", "b2", "b2", "b2", "b2", "b2", "b2", "b2", "b2", 
    "Child's date of birth (cmc)",      "b3", "b3", "b3", "b3", "b3", "b3", "b3", "b3", "b3", 
    "Child's sex",                      "b4", "b4", "b4", "b4", "b4", "b4", "b4", "b4", "b4", 
    "Preceding birth interval",         "b11", "b11", "b11", "b11", "b11", "b11", "b11", "b11", "b11", 
    "Mother-level variables",           NA, NA, NA, NA, NA, NA, NA, NA, NA, 
    "Mother's date of birth (cmc)",     "v011", "v011", "v011", "v011", "v011", "v011", "v011", "v011", "v011", 
    "Highest education level",          "v106", "v106", "v106", "v106", "v106", "v106", "v106", "v106", "v106", 
    "Current marital status",           "v501", "v501", "v501", "v501", "v501", "v501", "v501", "v501", "v501", 
    "Partner's education level",        "v701", "v701", "v701", "v701", "v701", "v701", "v701", "v701", "v701", 
    "Mother's anemia level",            NA, NA, NA, NA, NA, NA, NA, NA, NA, 
    "Respondent's weight in kg",        NA, NA, NA, NA, NA, NA, NA, NA, NA, 
    "Respondent's height in cm",        NA, NA, NA, NA, NA, NA, NA, NA, NA, 
    "Household-level variables",        NA, NA, NA, NA, NA, NA, NA, NA, NA, 
    "Sex of household head",            "v151", "v151", "v151", "v151", "v151", "v151", "v151", "v151", "v151", 
    "Age of household head",            "v152", "v152", "v152", "v152", "v152", "v152", "v152", "v152", "v152", 
    "Wealth index quintile",            NA, NA, NA, "v190", "v190", "v190", "v190", "v190", "v190", 
    "Social group variables",           NA, NA, NA, NA, NA, NA, NA, NA, NA,
    "Religion",                         "v130", "v130", "v130", "v130", "v130", "v130", "v130", "v130", "v130",
    "Caste",                            NA, NA, NA, NA, NA, NA, NA, NA, NA,
    "Ethnicity",                        NA, NA, NA, NA, NA, NA, NA, NA, NA,
    "Language of questionnaire",        NA, NA, NA, NA, NA, NA, NA, NA, NA,
    "Language of interview",            NA, NA, NA, NA, NA, NA, NA, NA, NA,
    "Native language of respondent",    NA, NA, NA, NA, NA, NA, NA, NA, NA,
    "Family-structure variables",       NA, NA, NA, NA, NA, NA, NA, NA, NA,
    "Relationship to hh head",          "hv101", "hv101", "hv101", "hv101", "hv101", "hv101", "hv101", "hv101", "hv101", 
    "De jure residents",                "hv102", "hv102", "hv102", "hv102", "hv102", "hv102", "hv102", "hv102", "hv102", 
    "De facto residents",               "hv103", "hv103", "hv103", "hv103", "hv103", "hv103", "hv103", "hv103", "hv103", 
    "Sex of hh member",                 "hv104", "hv104", "hv104", "hv104", "hv104", "hv104", "hv104", "hv104", "hv104", 
    "Age of hh member",                 "hv105", "hv105", "hv105", "hv105", "hv105", "hv105", "hv105", "hv105", "hv105", 
    "Highest education of hh member",   "hv106", "hv106", "hv106", "hv106", "hv106", "hv106", "hv106", "hv106", "hv106", 
    "Community-level variables",        NA, NA, NA, NA, NA, NA, NA, NA, NA,
    "Distance to healthcare facility",  "v467", "v467", "v467", "v467", "v467", "v467", "v467", "v467", "v467", 
    "Covered by health insurance",      "v481", "v481", "v481", "v481", "v481", "v481", "v481", "v481", "v481", 
    "Cluster altitude",                 NA, NA, NA, NA, NA, NA, NA, NA, NA,
) |> 
  mutate(pos = row_number(), .before = 1)

```

```{r}
#| label: tbl-checklist-bd
#| echo: false
#| output: true
#| tbl-cap: "Checklist of variables in Bangladesh DHS"

# Define the column names to check for non-missing values
year_cols <- names(bddhs)[grepl("^bd_", names(bddhs))]

# Create flextable
bddhs_ft <- bddhs |> 
  flextable() |> 
  set_header_labels(
    var_name = "Variable labels",
    bd_1993 = "BDDHS 1993",
    bd_1996 = "BDDHS 1996",
    bd_1999 = "BDDHS 1999",
    bd_2004 = "BDDHS 2004",
    bd_2007 = "BDDHS 2007",
    bd_2011 = "BDDHS 2011",
    bd_2014 = "BDDHS 2014",
    bd_2017 = "BDDHS 2017",
    bd_2022 = "BDDHS 2022"
  ) |> 
  # bold and italicize section headers
  bold(i = c(1, 10, 14, 23, 31, 35, 42, 49), part = "body") |> 
  italic(i = c(1, 10, 14, 23, 31, 35, 42, 49), part = "body")

# Loop through each year column and apply bg to non-NA cells
for (col in year_cols) {
  bddhs_ft <- bddhs_ft |>
    bg(i = which(!is.na(bddhs[[col]])), j = col, bg = "lightgreen")
}

# Print flextable
bddhs_ft

```

# India variable checklist

The variable availability for India is given below.

```{r}
#| label: data-checklist-ia
#| echo: false
#| output: false

# We create the data of the IADHS dataset
iadhs <- tribble(
    ~var_name, ~ia_1992, ~ia_1998, ~ia_2005, ~ia_2015, ~ia_2019,
    "ID and Weight variables",          NA, NA, NA, NA, NA, 
    "Women's ind sample weight",        "v005", "v005", "v005", "v005", "v005", 
    "Primary sampling unit",            "v021", "v021", "v021", "v021", "v021", 
    "Sample stratum number",            "v022", "v022", "v022", "v022", "v022", 
    "Strata used in sample design",     "v023", "v023", "v023", "v023", "v023", 
    "Cluster number",                   "v001", "v001", "v001", "v001", "v001", 
    "Household number",                 "v002", "v002", "v002", "v002", "v002", 
    "Respondent's line number",         "v003", "v003", "v003", "v003", "v003", 
    "Birth order",                      "bord", "bord", "bord", "bord", "bord", 
    "Sub-national region vars",         NA, NA, NA, NA, NA,
    "Region/Division",                  "v024", "v024", "v024", "v024", "v024", 
    "District of residence",            "sdistrict", "sdistri", "sdistri", "sdistri", "sdistri", 
    "Ecological region",                NA, NA, NA, NA, NA,
    "Birth history variables",          NA, NA, NA, NA, NA,
    "Survival status of child",         "b5", "b5", "b5", "b5", "b5", 
    "Child's age at death (cmc)",       "b7", "b7", "b7", "b7", "b7", 
    "Child is twin",                    "b0", "b0", "b0", "b0", "b0", 
    "Child's month of birth",           "b1", "b1", "b1", "b1", "b1", 
    "Child's year of birth",            "b2", "b2", "b2", "b2", "b2", 
    "Child's date of birth (cmc)",      "b3", "b3", "b3", "b3", "b3", 
    "Child's sex",                      "b4", "b4", "b4", "b4", "b4", 
    "Preceding birth interval",         "b11", "b11", "b11", "b11", "b11", 
    "Mother-level variables",           NA, NA, NA, NA, NA,
    "Mother's date of birth (cmc)",     "v011", "v011", "v011", "v011", "v011", 
    "Highest education level",          "v106", "v106", "v106", "v106", "v106", 
    "Current marital status",           "v501", "v501", "v501", "v501", "v501", 
    "Partner's education level",        "v701", "v701", "v701", "v701", "v701", 
    "Mother's anemia level",            NA, NA, NA, NA, NA,
    "Respondent's weight in kg",        NA, NA, NA, NA, NA,
    "Respondent's height in cm",        NA, NA, NA, NA, NA,
    "Household-level variables",        NA, NA, NA, NA, NA,
    "Sex of household head",            "v151", "v151", "v151", "v151", "v151", 
    "Age of household head",            "v152", "v152", "v152", "v152", "v152", 
    "Wealth index quintile",            NA, NA, "v190", "v190", "v190", 
    "Social group variables",           NA, NA, NA, NA, NA,
    "Religion",                         "v130", "v130", "v130", "v130", "v130",
    "Caste",                            "s116", "s116", "s116", "s116", "s116",
    "Ethnicity",                        NA, NA, NA, NA, NA,
    "Language of questionnaire",        NA, NA, NA, NA, NA,
    "Language of interview",            NA, NA, NA, NA, NA,
    "Native language of respondent",    NA, NA, NA, NA, NA,
    "Family-structure variables",       NA, NA, NA, NA, NA,
    "Relationship to hh head",          "hv101", "hv101", "hv101", "hv101", "hv101", 
    "De jure residents",                "hv102", "hv102", "hv102", "hv102", "hv102", 
    "De facto residents",               "hv103", "hv103", "hv103", "hv103", "hv103", 
    "Sex of hh member",                 "hv104", "hv104", "hv104", "hv104", "hv104", 
    "Age of hh member",                 "hv105", "hv105", "hv105", "hv105", "hv105", 
    "Highest education of hh member",   "hv106", "hv106", "hv106", "hv106", "hv106", 
    "Community-level variables",        NA, NA, NA, NA, NA,
    "Distance to healthcare facility",  "v467", "v467", "v467", "v467", "v467", 
    "Covered by health insurance",      "v481", "v481", "v481", "v481", "v481", 
    "Cluster altitude",                 NA, NA, NA, NA, NA
) |> 
  mutate(pos = row_number(), .before = 1)

```

```{r}
#| label: tbl-checklist-ia
#| echo: false
#| output: true
#| tbl-cap: "Checklist of variables in India DHS"

# Define the column names to check for non-missing values
year_cols <- names(iadhs)[grepl("^ia_", names(iadhs))]

# We create the data of the IADHS dataset
iadhs_ft <- iadhs |> 
    flextable() |> 
    set_header_labels(
        var_name = "Variable labels",
        ia_1992 = "IADHS 1992",
        ia_1998 = "IADHS 1998",
        ia_2005 = "IADHS 2005",
        ia_2015 = "IADHS 2015",
        ia_2019 = "IADHS 2019"
    ) |> 
  # bold and italicize section headers
  bold(i = c(1, 10, 14, 23, 31, 35, 42, 49), part = "body") |> 
  italic(i = c(1, 10, 14, 23, 31, 35, 42, 49), part = "body")

# Loop through each year column and apply bg to non-NA cells
for (col in year_cols) {
  iadhs_ft <- iadhs_ft |>
    bg(i = which(!is.na(iadhs[[col]])), j = col, bg = "lightgreen")
}

# Print flextable
iadhs_ft

```

# Maldives variable checklist

The variable availability for Maldives is given below.

```{r}
#| label: data-checklist-mv
#| echo: false
#| output: false

# We create the data of the MVDHS dataset
mvdhs <- tribble(
    ~var_name, ~mv_2009, ~mv_2016,
    "ID and Weight variables",          NA, NA,
    "Women's ind sample weight",        "v005", "v005", 
    "Primary sampling unit",            "v021", "v021", 
    "Sample stratum number",            "v022", "v022", 
    "Strata used in sample design",     "v023", "v023", 
    "Cluster number",                   "v001", "v001", 
    "Household number",                 "v002", "v002", 
    "Respondent's line number",         "v003", "v003", 
    "Birth order",                      "bord", "bord", 
    "Sub-national region vars",         NA, NA,
    "Region/Division",                  "v024", "v024", 
    "District of residence",            "sdistrict", "sdistrict", 
    "Ecological region",                NA, NA, 
    "Birth history variables",          NA, NA, 
    "Survival status of child",         "b5", "b5", 
    "Child's age at death (cmc)",       "b7", "b7", 
    "Child is twin",                    "b0", "b0", 
    "Child's month of birth",           "b1", "b1", 
    "Child's year of birth",            "b2", "b2", 
    "Child's date of birth (cmc)",      "b3", "b3", 
    "Child's sex",                      "b4", "b4", 
    "Preceding birth interval",         "b11", "b11", 
    "Mother-level variables",           NA, NA,
    "Mother's date of birth (cmc)",     "v011", "v011", 
    "Highest education level",          "v106", "v106", 
    "Current marital status",           "v501", "v501", 
    "Partner's education level",        "v701", "v701", 
    "Mother's anemia level",            NA, NA,
    "Respondent's weight in kg",        NA, NA,
    "Respondent's height in cm",        NA, NA,
    "Household-level variables",        NA, NA, 
    "Sex of household head",            "v151", "v151", 
    "Age of household head",            "v152", "v152", 
    "Wealth index quintile",            "v190", "v190", 
    "Social group variables",           NA, NA,
    "Religion",                         "v130", "v130",
    "Caste",                            NA, NA,
    "Ethnicity",                        NA, NA,
    "Language of questionnaire",        NA, NA,
    "Language of interview",            NA, NA,
    "Native language of respondent",    NA, NA,
    "Family-structure variables",       NA, NA,
    "Relationship to hh head",          "hv101", "hv101",
    "De jure residents",                "hv102", "hv102",
    "De facto residents",               "hv103", "hv103",
    "Sex of hh member",                 "hv104", "hv104",
    "Age of hh member",                 "hv105", "hv105",
    "Highest education of hh member",   "hv106", "hv106",
    "Community-level variables",        NA, NA,
    "Distance to healthcare facility",  "v467", "v467", 
    "Covered by health insurance",      "v481", "v481",
    "Cluster altitude",                 NA, NA
) |> 
  mutate(pos = row_number(), .before = 1)

```

```{r}
#| label: tbl-checklist-mv
#| echo: false
#| output: true
#| tbl-cap: "Checklist of variables in Maldives DHS"

# Define the column names to check for non-missing values
year_cols <- names(mvdhs)[grepl("^mv_", names(mvdhs))]

# We create the data of the MVDHS dataset
mvdhs_ft <- mvdhs |> 
    flextable() |> 
    set_header_labels(
        var_name = "Varmvble labels",
        mv_2009 = "MVDHS 2009",
        mv_2016 = "MVDHS 2016"
    ) |> 
  # bold and italicize section headers
  bold(i = c(1, 10, 14, 23, 31, 35, 42, 49), part = "body") |> 
  italic(i = c(1, 10, 14, 23, 31, 35, 42, 49), part = "body")

# Loop through each year column and apply bg to non-NA cells
for (col in year_cols) {
  mvdhs_ft <- mvdhs_ft |>
    bg(i = which(!is.na(mvdhs[[col]])), j = col, bg = "lightgreen")
}

# Print flextable
mvdhs_ft

```

# Nepal variable checklist

The variable availability for Nepal is given below.

```{r}
#| label: data-checklist-np
#| echo: false
#| output: false

# We create the data of the NPDHS dataset
npdhs <- tribble(
    ~var_name, ~np_1996, ~np_2001, ~np_2006, ~np_2011, ~np_2016, ~np_2022,
    "ID and Weight variables",          NA, NA, NA, NA, NA, NA, 
    "Women's ind sample weight",        "v005", "v005", "v005", "v005", "v005", "v005", 
    "Primary sampling unit",            "v021", "v021", "v021", "v021", "v021", "v021",
    "Sample stratum number",            "v022", "v022", "v022", "v022", "v022", "v022",
    "Strata used in sample design",     "v023", "v023", "v023", "v023", "v023", "v023",
    "Cluster number",                   "v001", "v001", "v001", "v001", "v001", "v001",
    "Household number",                 "v002", "v002", "v002", "v002", "v002", "v002",
    "Respondent's line number",         "v003", "v003", "v003", "v003", "v003", "v003",
    "Birth order",                      "bord", "bord", "bord", "bord", "bord", "bord", 
    "Sub-national region vars",         NA, NA, NA, NA, NA, NA,
    "Region/Division",                  "v024", "v024", "v024", "v024", "v024", "v024",
    "District of residence",            "sdistrict", "sdistrict", "sdistrict", "sdistrict", "sdistrict", "sdistrict", 
    "Ecological region",                NA, NA, NA, NA, NA, NA,
    "Birth history variables",          NA, NA, NA, NA, NA, NA,
    "Survival status of child",         "b5", "b5", "b5", "b5", "b5", "b5", 
    "Child's age at death (cmc)",       "b7", "b7", "b7", "b7", "b7", "b7", 
    "Child is twin",                    "b0", "b0", "b0", "b0", "b0", "b0", 
    "Child's month of birth",           "b1", "b1", "b1", "b1", "b1", "b1", 
    "Child's year of birth",            "b2", "b2", "b2", "b2", "b2", "b2", 
    "Child's date of birth (cmc)",      "b3", "b3", "b3", "b3", "b3", "b3", 
    "Child's sex",                      "b4", "b4", "b4", "b4", "b4", "b4", 
    "Preceding birth interval",         "b11", "b11", "b11", "b11", "b11", "b11", 
    "Mother-level variables",           NA, NA, NA, NA, NA, NA, 
    "Mother's date of birth (cmc)",     "v011", "v011", "v011", "v011", "v011", "v011", 
    "Highest education level",          "v106", "v106", "v106", "v106", "v106", "v106", 
    "Current marital status",           "v501", "v501", "v501", "v501", "v501", "v501", 
    "Partner's education level",        "v701", "v701", "v701", "v701", "v701", "v701",
    "Mother's anemia level",            NA, NA, NA, NA, NA, NA, 
    "Respondent's weight in kg",        NA, NA, NA, NA, NA, NA, 
    "Respondent's height in cm",        NA, NA, NA, NA, NA, NA, 
    "Household-level variables",        NA, NA, NA, NA, NA, NA,
    "Sex of household head",            "v151", "v151", "v151", "v151", "v151", "v151",
    "Age of household head",            "v152", "v152", "v152", "v152", "v152", "v152",
    "Wealth index quintile",            "v190", "v190", "v190", "v190", "v190", "v190",
    "Social group variables",           NA, NA, NA, NA, NA, NA,
    "Religion",                         "v130", "v130", "v130", "v130", "v130", "v130",
    "Caste",                            NA, NA, NA, NA, NA, NA,
    "Ethnicity",                        NA, NA, NA, NA, NA, NA,
    "Language of questionnaire",        NA, NA, NA, NA, NA, NA,
    "Language of interview",            NA, NA, NA, NA, NA, NA,
    "Native language of respondent",    NA, NA, NA, NA, NA, NA,
    "Family-structure variables",       NA, NA, NA, NA, NA, NA,
    "Relationship to hh head",          "hv101", "hv101", "hv101", "hv101", "hv101", "hv101",
    "De jure residents",                "hv102", "hv102", "hv102", "hv102", "hv102", "hv102",
    "De facto residents",               "hv103", "hv103", "hv103", "hv103", "hv103", "hv103",
    "Sex of hh member",                 "hv104", "hv104", "hv104", "hv104", "hv104", "hv104",
    "Age of hh member",                 "hv105", "hv105", "hv105", "hv105", "hv105", "hv105",
    "Highest education of hh member",   "hv106", "hv106", "hv106", "hv106", "hv106", "hv106",
    "Community-level variables",        NA, NA, NA, NA, NA, NA,
    "Distance to healthcare facility",  "v467", "v467", "v467", "v467", "v467", "v467",  
    "Covered by health insurance",      "v481", "v481", "v481", "v481", "v481", "v481", 
    "Cluster altitude",                 NA, NA, NA, NA, NA, NA
) |> 
  mutate(pos = row_number(), .before = 1)

```

```{r}
#| label: tbl-checklist-np
#| echo: false
#| output: true
#| tbl-cap: "Checklist of variables in Nepal DHS"

# Define the column names to check for non-missing values
year_cols <- names(npdhs)[grepl("^np_", names(npdhs))]

# We create the data of the NPDHS dataset
npdhs_ft <- npdhs |> 
    flextable() |> 
    set_header_labels(
        var_name = "Variable labels",
        np_1996 = "NPDHS 1996",
        np_2001 = "NPDHS 2001",
        np_2006 = "NPDHS 2006",
        np_2011 = "NPDHS 2011",
        np_2016 = "NPDHS 2016",
        np_2022 = "NPDHS 2022"
    ) |> 
  # bold and italicize section headers
  bold(i = c(1, 10, 14, 23, 31, 35, 42, 49), part = "body") |> 
  italic(i = c(1, 10, 14, 23, 31, 35, 42, 49), part = "body")

# Loop through each year column and apply bg to non-NA cells
for (col in year_cols) {
  npdhs_ft <- npdhs_ft |>
    bg(i = which(!is.na(npdhs[[col]])), j = col, bg = "lightgreen")
}

# Print flextable
npdhs_ft

```

# Pakistan variable checklist

The variable availability for Pakistan is given below.

```{r}
#| label: data-checklist-pk
#| echo: false
#| output: false

# We create the data of the PKDHS dataset
pkdhs <- tribble(
    ~var_name, ~pk_1990, ~pk_2006, ~pk_2012, ~pk_2017,
    "ID and Weight variables",          NA, NA, NA, NA,
    "Women's ind sample weight",        "v005", "v005", "v005", "v005",
    "Primary sampling unit",            "v021", "v021", "v021", "v021",
    "Sample stratum number",            "v022", "v022", "v022", "v022",
    "Strata used in sample design",     "v023", "v023", "v023", "v023",
    "Cluster number",                   "v001", "v001", "v001", "v001",
    "Household number",                 "v002", "v002", "v002", "v002",
    "Respondent's line number",         "v003", "v003", "v003", "v003",
    "Birth order",                      "bord", "bord", "bord", "bord",
    "Sub-national region vars",         NA, NA, NA, NA,
    "Region/Division",                  "v024", "v024", "v024", "v024",
    "District of residence",            "sdistri", "sdistri", "sdistri", "sdistri",
    "Ecological region",                NA, NA, NA, NA,
    "Birth history variables",          NA, NA, NA, NA,
    "Survival status of child",         "b5", "b5", "b5", "b5",
    "Child's age at death (cmc)",       "b7", "b7", "b7", "b7",
    "Child is twin",                    "b0", "b0", "b0", "b0",
    "Child's month of birth",           "b1", "b1", "b1", "b1",
    "Child's year of birth",            "b2", "b2", "b2", "b2",
    "Child's date of birth (cmc)",      "b3", "b3", "b3", "b3",
    "Child's sex",                      "b4", "b4", "b4", "b4",
    "Preceding birth interval",         "b11", "b11", "b11", "b11",
    "Mother-level variables",           NA, NA, NA, NA,
    "Mother's date of birth (cmc)",     "v011", "v011", "v011", "v011",
    "Highest education level",          "v106", "v106", "v106", "v106",
    "Current marital status",           "v501", "v501", "v501", "v501",
    "Partner's education level",        "v701", "v701", "v701", "v701",
    "Mother's anemia level",            NA, NA, NA, NA,
    "Respondent's weight in kg",        NA, NA, NA, NA,
    "Respondent's height in cm",        NA, NA, NA, NA,
    "Household-level variables",        NA, NA, NA, NA,
    "Sex of household head",            "v151", "v151", "v151", "v151",
    "Age of household head",            "v152", "v152", "v152", "v152",
    "Wealth index quintile",            "v190", "v190", "v190", "v190",
    "Social group variables",           NA, NA, NA, NA,
    "Religion",                         NA, NA, NA, NA,
    "Caste",                            NA, NA, NA, NA,
    "Ethnicity",                        NA, NA, NA, NA,
    "Language of questionnaire",        NA, NA, NA, NA,
    "Language of interview",            NA, NA, NA, NA,
    "Native language of respondent",    NA, NA, NA, NA,
    "Family-structure variables",       NA, NA, NA, NA,
    "Relationship to hh head",          "hv101", "hv101", "hv101", "hv101",
    "De jure residents",                "hv102", "hv102", "hv102", "hv102",
    "De facto residents",               "hv103", "hv103", "hv103", "hv103",
    "Sex of hh member",                 "hv104", "hv104", "hv104", "hv104",
    "Age of hh member",                 "hv105", "hv105", "hv105", "hv105",
    "Highest education of hh member",   "hv106", "hv106", "hv106", "hv106",
    "Community-level variables",        NA, NA, NA, NA,
    "Distance to healthcare facility",  "v467", "v467", "v467", "v467", 
    "Covered by health insurance",      "v481", "v481", "v481", "v481",
    "Cluster altitude",                 NA, NA, NA, NA
) |> 
  mutate(pos = row_number(), .before = 1)

```

```{r}
#| label: tbl-checklist-pk
#| echo: false
#| output: true
#| tbl-cap: "Checklist of variables in Pakistan DHS"

# Define the column names to check for non-missing values
year_cols <- names(pkdhs)[grepl("^pk_", names(pkdhs))]

# We create the data of the PKDHS dataset
pkdhs_ft <- pkdhs |> 
    flextable() |> 
    set_header_labels(
        var_name = "Variable labels",
        pk_1990 = "PKDHS 1990",
        pk_2006 = "PKDHS 2006",
        pk_2012 = "PKDHS 2012",
        pk_2017 = "PKDHS 2017"
    ) |> 
  # bold and italicize section headers
  bold(i = c(1, 10, 14, 23, 31, 35, 42, 49), part = "body") |> 
  italic(i = c(1, 10, 14, 23, 31, 35, 42, 49), part = "body")

# Loop through each year column and apply bg to non-NA cells
for (col in year_cols) {
  pkdhs_ft <- pkdhs_ft |>
    bg(i = which(!is.na(pkdhs[[col]])), j = col, bg = "lightgreen")
}

# Print flextable
pkdhs_ft

```

